### 2015-08-11 Projects/DelCo_2015/Report/Test_Matrix.tex
Delco_2015: update test matrix table

\begin{sidewaystable}[htbp]
\centering
\captionof{table}{DelCo ESTC 2015 Tests}\label{tab:tests}
\begin{tabular}{lllll}
\toprule[1.5pt]
Test \#         &  Vent Configuration         	& Attack           & Hose Stream                         & Gear      \\
\midrule
30              &  Cherry Road                	& Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
31              &  Cherry Road; single basement & Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
32              &  Cherry Road + upper C doors  & Uncoordinated    &  Straight, 120~gpm                  & 2 samples \\
33              &  PPV Test                     & & &           \\  
34              &  Cherry Road                  & Coordinated      &  Straight, 120~gpm                  & 3 samples \\   
35              &  Cherry Road + PPV            & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples \\
36              &  Cherry Road                  & Coordinated      &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
37              &  Cherry Road                  & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
38              &  Open A door + C doors        &                  &  Straight, CAFS, 120~gpm            & 3 samples + facepieces \\
39				&  Open A door + C doors        &                  &  Straight, 130~gpm                  & \\
40				&  Open A door + C doors        &                  &  Straight, CAFS, 130~gpm            & \\
41				&  Open A door + C doors        &                  &  CAFS, varied                       & \\
42				&  Cherry Road + upper C doors  & Allow decay      &  Straight, 150~gpm                  & \\
43				&  Open A door + C doors        &                  &  Straight/narrow fog, 120/180~gpm   & 1 sample \\
44				&  Open A door + C doors        &                  &  Interior wide fog, 130~gpm         & 1 sample, facepiece \\
45              &  Open A door + C doors        & Delay water 44   &  Interior wide fog, 130~gpm         & 1 sample, facepiece, helmet \\
45              &  Cherry Road; single basement & Uncoordinated    &  Straight, 150~gpm					 & \\
\bottomrule[1.25pt]
\end{tabular}
\end{sidewaystable}

>>>>

\begin{sidewaystable}[htbp]
\centering
\captionof{table}{DelCo ESTC 2015 Tests}\label{tab:tests}
\begin{tabular}{lllll}
\toprule[1.5pt]
Test \#         &  Vent Configuration         	& Attack           & Hose Stream                         & Gear      \\
\midrule
30 West         &  Cherry Road                	& Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
31 West         &  Cherry Road; single basement & Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
32 West         &  Cherry Road + upper C doors  & Uncoordinated    &  Straight, 120~gpm                  & 2 samples \\
33 West         &  PPV Test                     & & &           \\  
34 West         &  Cherry Road                  & Coordinated      &  Straight, 120~gpm                  & 3 samples \\   
35 West         &  Cherry Road + PPV            & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples \\
36 West         &  Cherry Road                  & Coordinated      &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
37 West         &  Cherry Road                  & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
38 West         &  Open A door + C doors        &                  &  Straight, CAFS, 120~gpm            & 3 samples + facepieces \\
39 West 		&  Open A door + C doors        &                  &  Straight, 130~gpm                  & \\
40 West 		&  Open A door + C doors        &                  &  Straight, CAFS, 130~gpm            & \\
41 West 		&  Open A door + C doors        &                  &  CAFS, varied                       & \\
42 West 		&  Cherry Road + upper C doors  & Allow decay      &  Piercing Nozzle, 150~gpm           & \\
43 West 		&  Open A door + C doors        &                  &  Straight/narrow fog, 120/180~gpm   & 1 sample \\
44 West 		&  Open A door + C doors        &                  &  Interior wide fog, 130~gpm         & 1 sample, facepiece \\
45 West         &  Open A door + C doors        & Delay water 44   &  Interior wide fog, 130~gpm         & 1 sample, facepiece, helmet \\
46 West         &  Cherry Road; single basement & Uncoordinated    &  Straight, 150~gpm					 & \\
47 West         &  Cherry Road					& Coordinated      &  Straight, 140~gpm					 & head forms \\
48 West         &  Cherry Road					& Uncoordinated    &  Straight, 180~gpm                  & head forms \\
49 East         &  C Doors                      & Sprinklered      & & \\
50 West         &  Cherry Road + Vertical		& Uncoordinated    &  Straight, 180~gpm                  & \\
51 East         &  C Doors                      & Sprinklered      & & \\
52 East			&  PPV Test 					& & &			\\
53 East			&  PPV Test 					& & &			\\
54 East			&  PPV Test 					& & &			\\
55 East			&  PPV Test 					& & &			\\
56 West			&  Cherry Road					& Coordinated	   &  Straight, 150~gpm					 & 3 samples + head forms \\ 
57 West			&  Cherry Road					& Uncoordinated	   &  Straight, 150~gpm					 & 3 samples + head forms \\
58 East			&  Single C door Open, A fire 	& C door    	   &  Straight, 150~gpm                  & \\
59 East         &  C window, A fire				& C window  	   &  Straight, 150~gpm					 & \\
60 West			&  Open C Doors 				& 				   &									 & 3 hose samples \\
61 East         &  C window, C fire             & C window         &  Wide fog, 150~gpm                  & \\
62 West			&  Open C Doors 				& 				   &									 & 3 hose samples \\
63 East         &  C window + window base       & C window         & Wide fog, 150~gpm 					 & \\

\bottomrule[1.25pt]
\end{tabular}
\end{sidewaystable}
